\documentclass[12pt]{scrbook}

\usepackage{boxedminipage}

\DeclareNewTOC[
type = infobox,
types = infoxboxes,
float,
name = Infobox,
counterwithin=chapter,
listname = {List of Infoboxes},
atbegin=\boxedminipage{\textwidth},
atend=\endboxedminipage
]{inf}

\begin{document}

\chapter{Testing the info box}

Here is some text I would have written before the info box. Here is some text I would have written before the info box. Here is some text I would have written before the info box. Here is some text I would have written before the info box. Here is some text I would have written before the info box. Here is some text I would have written before the info box. Here is some text I would have written before the info box. Here is some text I would have written before the info box. Here is some text I would have written before the info box. Here is some text I would have written before the info box.

\begin{infobox}[!htb]
\caption{Testing}
	Here is some content in the info box. Here is some content in the info box. Here is some content in the info box. Here is some content in the info box. 
\end{infobox}

Here is some text I would have written after but still related to the info box. Here is some text I would have written after but still related to the info box. Here is some text I would have written after but still related to the info box. Here is some text I would have written after but still related to the info box. Here is some text I would have written after but still related to the info box. Here is some text I would have written after but still related to the info box. Here is some text I would have written after but still related to the info box.

\end{document}
